### 2015-03-02 fundamentals/impl.tex
addresses the concern that mention of the resource exchange may blindside readers. This was suggested by Erich Schneider. The original comment was ' This may blindside readers, as the resource exchange has not yet been introduced.  Maybe this level of information need not be provided here'

The architecture of \Cyclus allows developers to define nuclear fuel cycle
processes independent of the simulation logic. To achieve this, agents are
developed to represent facilities, institutions, and regions comprising the
nuclear fuel cycle. These agents are created using the \Cyclus framework
\gls{API}, a set of functions and protocols which assist in agent development
and specify how agents should be defined.  This encapsulated `plug-in' design
choice provides two major benefits. First, analysts can take advantage of the
simulation logic \gls{API} and archetype ecosystem when they apply \Cyclus to
their specific problem.  A modeler can focus on creating or customizing
nuclear facility, institution, resource, and toolkit models within their
specific area of technical expertise. Second, because \Cyclus uses a modular
archetype approach, comparing two archetypes is straightforward. For example, if
an analyst would like to compare the effect of using different models to
determine the input fuel composition for fast reactors, fuel
fabrication archetypes can be developed and interchanged while keeping the rest
of the models used in the simulation fixed.

@@

Cyclopts \cite{gidden_cyclopts_2015}, a proof of principle design and
implementation of a \Cyclus-enabled application on such a large computer system,
uses UW-Madison's HTCondor \gls{HTC} infrastructure to perform sensitivity
studies on \Cyclus' resource exchange optimization solvers. Cyclopts has run over $10^5$ jobs, comprising more than 60,000 total compute hours,
using the \Cyclus library via its resource exchange \gls{API}.  The \gls{HTC}
infrastructure has separately been utilized to run and collect information from
full \Cyclus simulations running in parallel on $10^3$ machines reliably for
order $10^5$ simulations.

>>>>

The architecture of \Cyclus allows developers to define nuclear fuel cycle
processes independent of the simulation logic. To achieve this, \emph{agents} are
developed which represent facilities, institutions, and regions comprising the
nuclear fuel cycle. These agents are created using the \Cyclus framework
\gls{API}, a set of functions and protocols which assist in agent development
and specify how agents should be defined.  This encapsulated `plug-in' design
choice provides two major benefits. First, analysts can take advantage of the
simulation logic \gls{API} and archetype ecosystem when they apply \Cyclus to
their specific problem.  A modeler can focus on creating or customizing
nuclear facility, institution, resource, and toolkit models within their
specific area of technical expertise. Second, because \Cyclus uses a modular
archetype approach, comparing two archetypes is straightforward. For example, if
an analyst would like to compare the effect of using different models to
determine the input fuel composition for fast reactors, fuel
fabrication archetypes can be developed and interchanged while keeping the rest
of the models used in the simulation fixed.

@@

Cyclopts \cite{gidden_cyclopts_2015}, a proof of principle design and
implementation of a \Cyclus-enabled application on such a large computer system,
uses UW-Madison's HTCondor \gls{HTC} infrastructure to perform sensitivity
studies. Cyclopts has run over $10^5$ jobs, comprising more than 60,000 total
compute hours. The \gls{HTC} infrastructure has separately been utilized to
run and collect information from full \Cyclus simulations running in parallel
on $10^3$ machines reliably for order $10^5$ simulations.
